Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-31 Paper/results.tex
Fixed decline and increase with flipped plots

To study changes over time, we first plotted the
number of border ASes required to intercept 90\% of in-to-out paths
for each year (\figurename \ref{fig:nodesFree} and \figurename
\ref{fig:nodesCensor}).  The results are striking with a steep decline
over time for some nations (China and Turkey) and increases for others
(Germany and France), while some countries remained relatively
stable. Given that the overall number of ASes and paths has increased
globally over time, it is likely that even nations that look stable
have in fact become more 'chokepointy' over time as some border nodes
must be intercepting more paths.  This fact makes the decline observed
for some countries even more striking.

>>>>

To study changes over time, we first plotted the
national chokepoint potential of each of the 8 selected countries
for each year (\figurename \ref{fig:nodesFree} and \figurename
\ref{fig:nodesCensor}).  The results are striking with a steep increase
over time for some nations (China and Turkey) and decreases for others
(Germany and France), while some countries remained relatively
stable. Given that the overall number of ASes and paths has increased
globally over time, it is likely that even nations that look stable
have in fact become more 'chokepointy' over time as some border ASes
must be intercepting more paths.  This fact makes the increased NCP observed
for some countries even more striking.
